Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-20 paper/paper.tex
pass on results

\begin{table}[h]
  \centering
  \caption{\label{tab:summary-hi}Number of \hi\ warning
    reports per engine.}
  \begin{tabular}{crrrr}
    \toprule
    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey \\
    \midrule
    \radamsa{} & & \\
    \quickfuzz{} & & \\    
    \bottomrule     
  \end{tabular}
\end{table}

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:false-positives}Distribution of false
    positives buckets per source.}
  \begin{tabular}{crr}
    \toprule
    & \radamsa\ & \quickfuzz\ \\
    Undefined & - & - \\
    Timeout/OME & - & - \\
    Not Implemented & - & - \\
    Upcoming Feature & - & - \\
    Error Message Mismatch & - & - \\    
    Invalid Input & - & - \\    
    \bottomrule     
  \end{tabular}
\end{table}

>>>>

\begin{table}[h]
  \centering
  \caption{\label{tab:summary-hi}Number of \hi\ warning
    reports per engine.}
  \begin{tabular}{crrrrr}
    \toprule
    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey & 2+\\
    \midrule
    \radamsa{} & 30 & 4 & 121 & 3 & 143\\
    \quickfuzz{} & & & & & \\    
    \bottomrule     
  \end{tabular}
\end{table}

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:false-positives}Distribution of false
    positives buckets per source.}
  \begin{tabular}{crr}
    \toprule
    & \radamsa\ & \quickfuzz\ \\
    Undefined & 18 & - \\
    Timeout/OME & 23 & - \\
    Not Implemented & 19 & - \\
    Upcoming Feature & - & - \\
    Error Message Mismatch & 3 & - \\    
    Invalid Input & 10 & - \\    
    \bottomrule     
  \end{tabular}
\end{table}
